\documentclass[./main.tex]{subfiles}

\begin{document}

\section{Conclusion}
In this report we compared simple local search, basic evolution algorithm and custom memetic algorith.

On simpler, smaller instances, the local search is better that the other two, because the search space is small enough and the algorithm has a chance to explore larger area and get to more promising solutions.
On harder instances, this does not hold and the local search does not provide good results.
Big advantage of local search is its speed.

The evolution algorithm needs more evaluations, but it eventually overcomes local search or at least gets on the same level.
On bigger instances, it starts to struggle from stagnation of population and cannot further improve.
Its huge disadvantage is, that it is by far the slowest from these three (time measured on the same number of evaluations).

The memetic algorithm quite struggles on smaller instances, as it cannot use the full potential of local search, but wastes a lot of evaluations on it, so it cannot breed as much.
However, on large and hard instances, it is superior to both other algorithms.
But, it needs more evaluations to overcome them, which is a big disadvatage.
On the other hand, it is faster than evolution algorithm on the same number of evaluations.
Also, it converges monotically while tightening interquartile range, so it is more likely to find similar solutions.

None of these algorithms struggles from being unable to find valid solution as it is usually quickly found in the first few iterations.

\end{document}

